### 2011-07-22 Text/paper.tex
Made a small report. Need to recalculate and to rerun everything.

The literature correlations of mass transfer dependence on the bubble velocities are presented in
Fig. \ref{fig:mass:transfer:theoretical}. Note, that the correlations presented in
Fig. \ref{fig:mass:transfer:theoretical} are used primarily for circular capillaries
(\citeauthor{vanbaten-circular,bercic-mass}) and for square capillaries (\citeauthor{yue-mass}). We
adapt these results for flow between parallel plates by using hydraulic
diameter \cite{bercic-mass} which can be calculated as:
\begin{equation}
d_h = \lim_{W\to\infty}\frac{4A}{P}=\lim_{W\to\infty}\frac{4 W\,H}{2(W+H)}=2 H.
\end{equation}
For comparison reasons we as well present the correlation when the hydraulic diameter is taken as
$d_h=H$, see Fig. \ref{fig:mass:transfer:theoretical}.

\begin{figure}[htb!]
\includegraphics[width=\textwidth]{Figures/theoretical_correlations.eps}\\
\includegraphics[width=\textwidth]{Figures/theoretical_correlations_without_hydraulic.eps}\\
\caption{The literature correlations by various authors with hydraulic diameter taken as $2 H$
(top) and $H$ (bottom). Correlations deviate a lot among each
other.\label{fig:mass:transfer:theoretical}}
\end{figure}

@@

\section{Simulation results}
\subsection{Steady-state}
Using Eq.\ref{main:simulation:equation} we calculated the mass transfer coefficient. One can see
the plots for the mass transfer coefficient versus time in Fig. \ref{fig:steady:state}. We state as
a steady-state condition the average of concentration values between $500000$ to $1000000$ time
steps.{\color{red} We need to put more time steps. As well it is probably connected with Fourier
number.} The average calculated volumetric mass transfer coefficients values are presented in Table
\ref{table:volumetric:coefficients}. For each of the measurements we as well provided the Fourier
number (for the flow between plates is as follows):
\begin{equation}
Fo=\frac{D t_{\mathrm{film}}}{\delta^2}=\frac{D
(L_{\mathrm{bubble}}-H)}{U_{\mathrm{bubble}}\delta^2}.
\end{equation}
\begin{figure}[htb!]
\includegraphics[width=\textwidth]{Figures/steady_state.eps}
\caption{The mass transfer coefficient vs. time iterations. One can see that the pseudo steady
state can be reached after $500000$. The mass transfer coefficient is taken as the average of
concentration values between $500000$ to $1000000$ time steps.\label{fig:steady:state}}
\end{figure}
\begin{table}[htb!]
\begin{tabularx}{\textwidth}{|X|X|X|}
\hline
$Ca$&$Fo$&$k_L a,\,\mathrm{s}^{-1}$\\
\hline
$0.026$&$0.08493$&$0.2737$\\
$0.047$&$0.02160$&$0.3664$\\
$0.080$&$0.00588$&$0.4959$\\
$0.065$&$0.00862$&$0.4734$\\
$0.222$&$0.00103$&$0.8505$\\
$0.479$&$0.00034$&$1.1541$\\
$0.736$&$0.00018$&$1.1801$\\
$0.989$&$0.00012$&$1.2215$\\
\hline
\end{tabularx}
\caption{Simulation results for different capillary numbers. \label{table:volumetric:coefficients}}
\end{table}

Comparison between correlations and simulations one can find in Fig.
\ref{fig:comparison:correlations}.
\begin{figure}[htb!]
\includegraphics[width=\textwidth]{Figures/comparison_correlations.eps}
\caption{One can see the comparison between correlations and simulations. {\color{red} Last two
points can be eliminated due to improper imposement of the concave structure of the bubble. The
large deviation of the results can be probably explained by the flow between plates in comparison
with the flow in circular and square microchannels.} \label{fig:comparison:correlations}}
\end{figure}

@@

@@

&-D\frac{\mathrm{d} C(x,t)}{\mathrm{d}x}|_{x=0}=D \frac{1}{\sqrt{D t}}\\
&k_L = \sqrt{\frac{D}{\pi t_{\mathrm{film}}}}.

@@

\item[Cylinder mass transfer] For the cylinder mass transfer one needs to solve the heat conduction
equation one needs to use cylindrical coordinates. The system is prescribed by the following set
of equations:
\begin{equation}
\begin{aligned}
&\frac{\partial C}{\partial t}=D\frac{\partial^2 C}{\partial r^2} + \frac{D}{r}\frac{\partial
C}{\partial r}\\
&C(a,t)=0\\
&C(r,0)=0\\
\end{aligned}
\end{equation}
The solution is given by \citet{ozisik} as:
\begin{equation}
\begin{aligned}
&C(r,t)=C_0\\
& - C_0\int_{\alpha=0}^{\infty}{\mathrm{d}\alpha \frac{\alpha}{J_0^2(\alpha
a)+Y_0^2(\alpha a)}e^{-\alpha^2 D t}[J_0(\alpha r) Y_0(\alpha a)-Y_0(\alpha r) J_0(\alpha a)]}\\
&\times \int_{r'=a}^{\infty}{r'[J_0(\alpha r')Y_0(\alpha a)-Y_0(\alpha r') J_0(\alpha
a)]\mathrm{d}r'}
\end{aligned}
\end{equation}
These integrals can be taken through the recurrent equations for Bessel functions.

>>>>

The literature correlations of mass transfer dependence on the bubble velocities are presented in
Fig. \ref{fig:mass:transfer:theoretical}. Note, that the correlations presented in
Fig. \ref{fig:mass:transfer:theoretical} are used primarily for circular capillaries
(\citeauthor{vanbaten-circular,bercic-mass}) and for square capillaries (\citeauthor{yue-mass}). We
adapt these results for flow between parallel plates by using hydraulic
diameter \cite{bercic-mass} which can be calculated as:
\begin{equation}
d_h = \lim_{W\to\infty}\frac{4A}{P}=\lim_{W\to\infty}\frac{4 W\,H}{2(W+H)}=2 H.
\end{equation}
For comparison reasons we derived in Section \ref{mass:transfer:correlation} the correlation for the
flow between plates, see Fig. \ref{fig:mass:transfer:theoretical}. One can see that the
difference is negligible.

\begin{figure}[htb!]
\includegraphics[width=\textwidth]{Figures/theoretical_correlations.eps}\\
%\includegraphics[width=\textwidth]{Figures/theoretical_correlations_without_hydraulic.eps}\\
\caption{The literature correlations by various authors.\label{fig:mass:transfer:theoretical}}
\end{figure}

@@

\section{Simulation results}
\subsection{Steady-state}
Using Eq.\ref{main:simulation:equation} we calculated the mass transfer coefficient. One can see
the plots for the mass transfer coefficient versus time in Fig. \ref{fig:steady:state}. We state as
a steady-state condition the average of concentration values between $500000$ to $1000000$ time
steps.{\color{red} We need to put more time steps. As well it is probably connected with Fourier
number.} The average calculated volumetric mass transfer coefficients values are presented in Table
\ref{table:volumetric:coefficients}. For each of the measurements we as well provided the Fourier
number (for the flow between plates is as follows):
\begin{equation}
Fo=\frac{D t_{\mathrm{film}}}{\delta^2}=\frac{D
(L_{\mathrm{bubble}}-H)}{U_{\mathrm{bubble}}\delta^2}.
\end{equation}
To understand the influence of the mass transfer in the film we provided the time needed for
diffusion to reach the film thickness distance (95\% confidence interval of the film thickness):
\begin{equation}
\delta\approx 2\sqrt{2}\sqrt{D t};\ t \approx \frac{\delta^2}{8 D};\ N_{iter}=\frac{t}{\Delta t}.
\end{equation}

\begin{figure}[htb!]
\includegraphics[width=\textwidth]{Figures/steady_state.eps}
\caption{The mass transfer coefficient vs. time iterations. One can see that the pseudo steady
state can be reached after $500000$. The mass transfer coefficient is taken as the average of
concentration values between $500000$ to $1000000$ time steps.\label{fig:steady:state}}
\end{figure}
\begin{table}[htb!]
\begin{tabularx}{\textwidth}{|X|X|X|X|}
\hline
$Ca$&$Fo$&$k_L a,\,\mathrm{s}^{-1}$&$N_{iter}$\\
\hline
$0.026$&$0.08493$&$0.2737$&$873984$\\
$0.047$&$0.02160$&$0.3664$&$1835817$\\
$0.080$&$0.00588$&$0.4959$&$3965227$\\
$0.065$&$0.00862$&$0.4734$&$3149710$\\
$0.222$&$0.00103$&$0.8505$&$8195770$\\
$0.479$&$0.00034$&$1.1541$&$12399627$\\
$0.736$&$0.00018$&$1.1801$&$14683652$\\
$0.989$&$0.00012$&$1.2215$&$16101062$\\
\hline
\end{tabularx}
\caption{Simulation results for different capillary numbers. \label{table:volumetric:coefficients}}
\end{table}

\subsection{Comparison between correlations and results}
Comparison between correlations and simulations one can find in Fig.
\ref{fig:comparison:correlations}. The simulated results exhibit larger mass transfer in comparison
with the given correlations. {\color{red} Need to recalculate and check the kinematic viscosities.}
\begin{figure}[htb!]
\includegraphics[width=\textwidth]{Figures/comparison_correlations.eps}
\caption{One can see the comparison between correlations and simulations. {\color{red} Last two
points can be eliminated due to improper imposement of the concave structure of the bubble. The
large deviation of the results can be probably explained by the flow between plates in comparison
with the flow in circular and square microchannels.} \label{fig:comparison:correlations}}
\end{figure}

@@

\label{mass:transfer:correlation}

@@

&-D\frac{\mathrm{d} C(x,t)}{\mathrm{d}x}|_{x=0}=D \frac{1}{\sqrt{\pi D t}}\\

@@

The accumulated concentration and the mass transfer coefficients are:
&\int_{0}^{t_{\mathrm{film}}}{-D\frac{\mathrm{d} C(x,t)}{\mathrm{d}x}|_{x=0} \mathrm{d}t}=2
\sqrt{ \frac{D t}{\pi}}\\
&k_L = 2 \sqrt{\frac{D}{\pi t_{\mathrm{film}}}}.
If we account for the two surfaces for the bubble then one can obtain the following volumetric mass
transfer coefficient:
&k_L a= 2\sqrt{\frac{D}{\pi t_{\mathrm{film}}}} 2
\frac{L_{\mathrm{bubble}}-(H_{\mathrm{eff}}-2\delta)}{(L_{\mathrm{bubble}}+L_{
\mathrm { slug } } )H_ { \mathrm { eff } } }\\
&k_L a= 2\sqrt{\frac{D}{\pi
\frac{L_{\mathrm{bubble}}-(H_{\mathrm{eff}}-2\delta)}{U_{\mathrm{bubble}}}}} 2
\frac{L_{\mathrm{bubble}}-(H_{\mathrm{eff}}-2\delta)}{(L_{\mathrm{bubble}}+L_{
\mathrm { slug } } )H_ { \mathrm { eff } } }\\
&k_L a=4 \sqrt{\frac{D U_{\mathrm{bubble}}}{\pi}}
\frac{\sqrt{L_{\mathrm{bubble}}-(H_{\mathrm{eff}-2\delta})}}{(L_{\mathrm{bubble}}+L_{\mathrm{slug}}
)H_ { \mathrm { eff } } }

\item[Cylinder mass transfer] For the cylinder mass transfer one needs to solve the heat conduction
equation one needs to use cylindrical coordinates. The system is prescribed by the following set
of equations:
\begin{equation}
\begin{aligned}
&\frac{\partial C}{\partial t}=D\frac{\partial^2 C}{\partial r^2} + \frac{D}{r}\frac{\partial
C}{\partial r}\\
&C(a,t)=0\\
&C(r,0)=0\\
\end{aligned}
\end{equation}
The solution is given by \citet{ozisik} as:
\begin{equation}
\begin{aligned}
&C(r,t)=C_0\\
& - C_0\int_{\alpha=0}^{\infty}{\mathrm{d}\alpha \frac{\alpha}{J_0^2(\alpha
a)+Y_0^2(\alpha a)}e^{-\alpha^2 D t}[J_0(\alpha r) Y_0(\alpha a)-Y_0(\alpha r) J_0(\alpha a)]}\\
&\times \int_{r'=a}^{\infty}{r'[J_0(\alpha r')Y_0(\alpha a)-Y_0(\alpha r') J_0(\alpha
a)]\mathrm{d}r'}
\end{aligned}
\end{equation}
These integrals can be taken through the recurrent equations for Bessel functions. However, the
penetration of the concentrator comes not only from the diffusion but mainly from the advection
part. According to the penetration theory one can use the following correlation for the mass
transfer coefficient:
\begin{equation}
k_L=2\sqrt{\frac{D}{\pi t_{\mathrm{contact}}}},
\end{equation}
where $t_{\mathrm{contact}}$ for the bubble cap can be calculated from the following considerations
\cite{vanbaten-circular}: the distance travelled by a fluid packet coming to the bubble equals to a
half of semicircle perimeter until it is swept away by the vortex in the front of the bubble
{\color{red} (working only for small capillary numbers where a vortex exists in the front of the
bubble)}. Therefore for the case of the bubble arising with the velocity $U_{\mathrm{bubble}}$ one
can estimate the mass transfer coefficient as follows:
\begin{equation}
k_L=2\sqrt{\frac{D}{\pi t_{\mathrm{contact}}}}=2\sqrt{\frac{D}{\pi \frac{ \pi
(H_{\mathrm{eff}}-2\delta)/2}{U_{\mathrm{bubble}}}}}=\frac{2\sqrt{2}}{\pi}\sqrt{\frac{D
U_{\mathrm{bubble}}}{H_{\mathrm{eff}}-2\delta}}
\end{equation}
The volumetric mass transfer coefficient is then as follows:
\begin{equation}
\begin{aligned}
k_L a=\frac{2\sqrt{2}}{\pi}\sqrt{\frac{D
U_{\mathrm{bubble}}}{H_{\mathrm{eff}}-2\delta}} \frac{\pi
(H_{\mathrm{eff}}-2\delta)}{(L_{\mathrm{bubble}}+L_{\mathrm{slug}}) H_{\mathrm{eff}}}\\
k_L a=2\sqrt{2}\sqrt{D
U_{\mathrm{bubble}}}\frac{\sqrt{H_{\mathrm{eff}}-2\delta}}{(L_{\mathrm{bubble}}+L_{\mathrm{slug}})H_
{\mathrm{eff}}}
\end{aligned}
\end{equation}

\end{description}
Therefore the overall adjusted for the flow between plates mass transfer coefficient is expressed as
follows:
\begin{equation}
\begin{aligned}
k_L a =&4 \sqrt{\frac{D U_{\mathrm{bubble}}}{\pi}}
\frac{\sqrt{L_{\mathrm{bubble}}-(H_{\mathrm{eff}-2\delta})}}{(L_{\mathrm{bubble}}+L_{\mathrm{slug}}
)H_ { \mathrm { eff } } }\\
&+2\sqrt{2}\sqrt{D
U_{\mathrm{bubble}}}\frac{\sqrt{H_{\mathrm{eff}}-2\delta}}{(L_{\mathrm{bubble}}+L_{\mathrm{slug}})H_
{\mathrm{eff}}}.
\end{aligned}
\end{equation}
